---
title: "TSA signal generator"
author: "omidalam"
date: "9/8/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(rtracklayer)
library(GenomicRanges)
library(ggplot2)
library(myfuncs)
```

# Intro

TSA_slope models TSA-seq signal by using polynomial fitting in different size windows. Upon polynomial approxiation, 
TSA_slopr can approximate TSA-seq slope by calculating the first order derivative of this approximation.
The center of a high slope region is determined by second derivative of this approximation.

Several parameters affect the behavior of this approximation.

+ bin size
+ Number of bins used for smoothing
+ Polynomial degre (has little effect beyond linear)

In this document I want to create different patterns of TSA-seq and see the effect on TSA-slope.

# Model signals
## flat-linear-flat
bin size: 20 kb
flat 1 mb which is 50 bin
linear 1 mb which 50 bin
flat 1 mb which 50 bin


```{r}
signal_pltr<-function(BW){
  BW_slp<-BW_slopr(BW,bin=NA,slop_wind = 20)
  BW_smth<-BW_smthr(BW,bin=NA,smth_wind =20)
  data<-data.frame(TSA_score=BW$score,TSA_smth=BW_smth$score,TSA_slp=BW_slp$score,Mbp=seq(1,tot_bins))
  all_plot<-ggplot(data = data)+geom_line(aes(x=Mbp,y=TSA_score,colour="TSA score"))+
    geom_point(aes(x=Mbp,y=TSA_smth,colour="TSA smooth"),size=0.3)+
    geom_line(aes(x=Mbp,y=TSA_slp*50,colour="TSA slope"))
  all_plot<-all_plot+scale_y_continuous(sec.axis = sec_axis(~./50, name = "TSA slope"))
  return(all_plot)
}
```
```{r}

bin<-2e4
flat<-50
linear<-100
tot_bins<-(2*flat+linear)
region_len<-tot_bins*bin

start_flat_val=-1.5
end_flat_val=1.5
flf<-GRanges(
  seqnames=Rle(c(rep("chr1",tot_bins))),
  ranges=IRanges(start=seq(1,region_len-bin+1, by=bin), width=bin),
  score=rep(0,tot_bins)
)


flf$score[1:flat-1]=start_flat_val
flf$score[(flat):(flat+linear)]=seq(start_flat_val,end_flat_val,length.out = linear+1)
flf$score[(flat+linear):tot_bins]=end_flat_val
flf$score<-flf$score+0.00001
seqlengths(flf)<-region_len

signal_pltr(flf)
```

```{r}

bin<-2e4
flat<-30
linear<-30
tot_bins<-(2*flat+linear)
region_len<-tot_bins*bin

start_flat_val=1.5
end_flat_val=-1.5
flf<-GRanges(
  seqnames=Rle(c(rep("chr1",tot_bins))),
  ranges=IRanges(start=seq(1,region_len-bin+1, by=bin), width=bin),
  score=rep(0,tot_bins)
)


flf$score[1:flat-1]=start_flat_val
flf$score[(flat):(flat+linear)]=seq(start_flat_val,end_flat_val,length.out = linear+1)
flf$score[(flat+linear):tot_bins]=end_flat_val
flf$score<-flf$score+0.00001
seqlengths(flf)<-region_len
signal_pltr(flf)+geom_vline(xintercept = tot_bins/2)
# View(flf$score)
```
